Combined annotation exploration for SCPCP000006

### 2025-02-27 analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
Update analyses/cell-type-wilms-tumor-06/notebook/07_combined_annotation_across_samples_exploration.Rmd
Co-authored-by: Stephanie Spielman <stephanie.spielman@gmail.com>

These five samples do not have enough immune and endothelium cell to be used as a normal reference in `scripts/06_infercnv.R` and we previously decided to run `scripts/06_infercnv.R` without any reference for these samples.
In that case, the mean expression profile over the sample is taken as the normal reference, biaising the inference of CNV.

@@

CNV_profile_gain <- cell_type_df_sub |>
  select(sample_id, contains("has_dupli_chr")) |>
  group_by(sample_id) |>
  summarise_all(.funs = mean) |>
  pivot_longer(cols = -sample_id) |>
  rename("chromosome_arm" = "name", "percentage" = "value") |>
  left_join( chromosome_arms, by = c("chromosome_arm"="dupli")) |>
  mutate(chromosome_arm = factor(chromosome_arm, levels = has_dupli_chr)) |>
  mutate(absolute_70 = case_when((percentage > 0.7) ~ 1,
         .default = 0),
         absolute_10 = case_when((percentage > 0.1) ~ 1,
         .default = 0))

>>>>

These five samples do not have enough immune and endothelium cell to be used as a normal reference in `scripts/06_infercnv.R` and we previously decided to run `scripts/06_infercnv.R` without any reference for these samples.
In that case, the mean expression profile over the sample is taken as the normal reference, biasing the inference of CNV.

@@

CNV_profile_gain <- cell_type_df_sub |>
  select(sample_id, contains("has_dupli_chr")) |>
  group_by(sample_id) |>
  summarise_all(.funs = mean) |>
  pivot_longer(cols = -sample_id) |>
  rename("chromosome_arm" = "name", "percentage" = "value") |>
  left_join( chromosome_arms, by = c("chromosome_arm"="dupli")) |>
  mutate(chromosome_arm = factor(chromosome_arm, levels = has_dupli_chr)) |>
  mutate(
    absolute_70 = ifelse(percentage > 0.7, 1, 0), 
    absolute_10 = ifelse(percentage > 0.1, 1, 0)
 )
